\documentclass[11pt]{article}                                   
\usepackage[utf8]{inputenc}                                     
\usepackage[T1]{fontenc}                                        
\usepackage{amsmath}                                            
\usepackage{amssymb}                                            
\usepackage{amsthm}                                             
\usepackage{mathtools}                                          
\usepackage{fixltx2e}                                           
\usepackage{longtable}                                          
\usepackage{float}                                              
\usepackage{array}                                              
\usepackage{multirow}                                           
\usepackage{multicol}                                           
\usepackage{wrapfig}                                            
\usepackage{rotating}                                           
\usepackage[normalem]{ulem}                                     
\usepackage{textcomp}                                           
\usepackage{marvosym}                                           
\usepackage{wasysym}                                            
\usepackage{hyperref}                                           
\tolerance=1000                                                 
\usepackage{caption}                                            
\usepackage{subcaption}                                         
\usepackage[margin=0.75in]{geometry}                            
\usepackage{enumerate}                                          
\usepackage{showexpl}                                           
\usepackage{color}                                              %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0}                            % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}                          
\newcommand{\todo}{{\LARGE \emph{\color{red}TODO}}}             
\hypersetup{                                                    
pdfkeywords={},                                                 
pdfsubject={}}                                                  
\newcounter{problem}                                            
\newcounter{solution}                                           
\usepackage{beramono}                                           
\usepackage{listings}                                           
\usepackage[usenames,dvipsnames]{xcolor}                        
\usepackage[T1]{fontenc}                                        
\usepackage{inconsolata}                                        
\usepackage{color}                                              
\definecolor{pblue}{rgb}{0.13,0.13,1}                           
\definecolor{pgreen}{rgb}{0,0.5,0}                              
\definecolor{pred}{rgb}{0.9,0,0}                                
\definecolor{pgrey}{rgb}{0.46,0.45,0.48}                        
\lstset{language=Java,                                          
showspaces=false,                                               
showtabs=false,                                                 
breaklines=true,                                                
showstringspaces=false,                                         
breakatwhitespace=true,                                         
commentstyle=\color{pgreen},                                    
keywordstyle=\color{pblue},                                     
stringstyle=\color{pred},                                       
basicstyle=\ttfamily,                                           
moredelim=[il][\textcolor{pgrey}]{$$},                          
moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}                   
}                                                               
% \parindent 0in
% \parskip 1em.
\begin{document}                                                
\title{EE 360P:\@Concurrent and Distributed Systems\\ Assignment 4}
\author{Student: Eric Crosson (email: eric.s.crosson@utexas.edu) \\
Student: William ``Stormy'' Mauldin (email: stormymauldin@utexas.edu)}
\date{\today}                                                   
\maketitle                                                      

\begin{enumerate}                                               
\item \textbf{(20 points)}                                      
\begin{enumerate}[(a)]                                          
\item Extend Lamport's mutex algorithm to solve $k$-mutual exclusion problem which allows at most $k$ processes to be in the critical section concurrently.

\begin{itemize}                                                 
\item \emph{Notes}: Each process keeps track of a counter $c$, representing the number of processes still allowed to enter the critical section, initialized to $k$.
\item To request the critical section, a process sends a timestamped message to all other processes and adds a timestamped request to the queue.
\item On receiving a request message, the request and its timestamp are stored in the queue and a timestamped acknowledgement is sent back.
\item To release the critical section, the process increments $c$ and sends a release message to all other processes.
\item On receiving a release message, the corresponding request is deleted from the queue.
\item A process determines that it can access the critical section if and only if all of the following are true:
\begin{itemize}                                                 
\item It has a request at the head of the queue                 
\item It has received a message from every other queued process.
\item $c > 0$                                                   
\end{itemize}                                                   
Immediately before entering the critical section, the process decrements $c$
\end{itemize}                                                   


\item Extend Ricart and Agrawala's mutex algorithm to solve the $k$-mutual exclusion problem.

\begin{itemize}                                                 
\item \emph{Notes}: Each process keeps track of a counter $c$, representing the number of processes still allowed to enter the critical section, initialized to $k$.
\item To request a resource, the process sends a timestamped message to all processes.
\item On receiving a request from any other process, the process sends an \emph{okay} message if either the process is not interested in the critical section or its own request has a higher timestamp value. Otherwise, that process is kept in a pending queue.
\item To release a resource, the process increments $c$ and sends \emph{okay} to all the process in the pending queue.
\item The process in the queue with timestamp $t$ is granted the resource when all of the it has requested the resource and all of the following are true:
\begin{itemize}                                                 
\item $(k-c)\leq t \leq(k-c+n)$, where $n$ = number of processes that responded to the \emph{request}
\item it has received the \emph{okay} message from every other process in response to its \emph{request} message
\item $c$ > 0                                                   
\end{itemize}                                                   
Immediately before entering the critical section, the process decrements $c$.
\end{itemize}                                                   

\end{enumerate}                                                 
\end{enumerate}                                                 
\end{document}                                                  
